Molecular dynamics simulation of synchronization in driven particles

### 2021-02-16 manuscript/manuscript_ajp_2020.tex
added pure dc sweep

We use a classical model for 
studying the dynamics of $N$ interacting particles,
using the net force on each particle to calculate
its trajectory.
Particles are confined in a two-dimensional (2D) 
simulation of area $A = L \times L$ where $L=36.5 a_0$
where $a_0$ is a dimensionless unit of length.
An individual particle $i$ has
position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$
and velocity $\vec{v}_i = d\vec{r}_i/dt$.
The edges of the system are treated with
periodic boundary conditions
such that a particle leaving the edge of the system is mapped
back to a position within the simulation boundaries 
by the transformation $x_i+L \rightarrow x_i$ and $y_i+L \rightarrow y_i$.
%and particles interact across PBC.
We show a schematic of the system in Fig.~\ref{fig:landscape0}(a).

@@

The molecular dynamics simulation is controlled by a $for()$ loop
which runs from an initial to maximum integer number of time steps.
%$t_i$.
Each integer time step interval %$t_{i+1}-t_i$
represents a simulation time of $\Delta t$ 
simulation units $\tau$.  %as described in Table 1
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}_i(t)$
and then integrate
the equation of motion to move particles
to an updated position.
%$\vec{r}_i(t+\Delta t)$.%
Since the acceleration as zero,
the integration of the equation of motion
is performed via 
the Euler method 
\begin{equation}
  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)
    \label{eq:euler}
\end{equation}
for a small time step $\Delta t = 0.01 \tau$.
In %Section~\ref{sec:problems}
Exercise~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%
The units of the simulated variables are summarized in Table ~\ref{tab:1}.

\begin{table}[h!]
\centering
\caption{Simulation parameters and units and comparable
  experimental values~\cite{Juniper2015}.
  Blanks %in the experimental parameters
  indicate
  units, rather than parameters that
  are not easily represented by a single value.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental value\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
temperature & $T_0 = 0$ \footnote{to learn more about the effects
  of temperature on this simulation
  see Ex.~\ref{ex:brownian} where we study the limit
  $U_0 \sim k_B T$.} & $T \sim 300K $ \\

@@

A single particle %on this landscape
responds to the applied driving force
by moving across the landscape %maxima
synchronized with 
the period of $F^D(t)$.
%applied driving force.
%along the y-direction
%({\it redundant, just refer back to eq. in Model?})
%and $V_{0y}=0.2$.
%This is illustrated in Fig.~\ref{fig:1}(a) where
%the red (blue) regions show local maxima (minima).
%
The numerical implementation of the landscape 
is calculated with Eq.~\ref{eq:ysubstrate} as 
\begin{equation}
  \label{eq:force}
  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
\end{equation}
where the force is scaled with parameter $A_{p} = N_p \pi U_0/L$.
In this section, we fix the landscape parameters
to $A_{p} = 0.1 F_0$ %force units
with $N_p=20$ minima %in the landscape
corresponding to a spatial period $\lambda = 1.825 a_0$.

%In Fig.~\ref{fig:0} 
The driven particle adjusts
its motion to traverse
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^D(t)$.
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
%
In Fig.~\ref{fig:0}(a)
we plot $F^D(t)$ %defined in Eq.~\ref{eq:drive}.
as a function of time with
%The time independent
constants $F^{dc}=0.1$, 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100 \tau$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%RAMP
%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$. at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$. In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^D(t)$ when the magnitude of the ac applied force is initially zero.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
-- i.e. $\sin{(\omega t)} = 1$.
%
%
%with the initial driving force at is minimum value 
%$F^D(0) = F^{dc}$. 
%
In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time.
We 
normalize $y$ by $\lambda$ %, the spatial period of the potential
to show  particle motion between substrate minima.  
The initial particle position is $y = 0 $. %1 a_0$,
%where the $F^l$ is negative.
%JUST BECAUSE
%causing the particle to move to
%a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
the motion of the particle
synchronizes with the driving period $T$.
We measure 
average particle velocity $\langle{v}_y\rangle$
as the average displacement %$\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
The particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ over the time period $T$,
with 
the average velocity 
$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
The horizontal dashed lines
coincide with the condition the particle is at a substrate minima
where substrate force  $F^l = -A_p$,  
i.e. $\sin{(\pi y / \lambda)} = 1$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
%Once the particle motion
%coincides with the applied drive,
%indicating synchronization,
The particle synchronizes its motion such that the 
driving force is maximum when the landscape 
force is minimum,
as indicated %with the coincidence of 
with the intersection of
vertical and horizontal lines.  
%i.e. the particle position $y/\lambda$.  
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $.

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single_particle.pdf}
\caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
  %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
  (b) 
  The $y-$position of the driven particle
  %of a single driven particle
  normalized by the period of the substrate $\lambda$.
  %as a function of time
  }
\label{fig:0}
\end{figure}
\end{center}

The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion. 
%In Fig.~\ref{fig:0}
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
%
The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.
  It is useful to compare
  mode-locked quantities %periodic signals
  in a two dimensional phase plot.
  In a non-driven system, an appropriate
  phase space is particle velocity $v_y$ versus position $y$.  
  In a system driven parallel to the $y-$direction,
  %the particle velocity and position increase
  %in time. % due to $F^{dc}$.
  %Since a system does not form
  %a closed loop in
  %$v_y$ vs $y$ space,
  we define phase variables 
  to account for the net increase in velocity
  and position.
  The phase position is
  defined as 
  %within the substrate period as 
  %We define a phase variable 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \phi(t) = 2\pi(y(t)-\langle v_y \rangle t)/\lambda
  \end{equation}
  centered about the average particle velocity $\langle v_y \rangle$
  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
  We plot this phase
  versus the phase velocity 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \dot{\phi}(t) = 2\pi(v_y(t)-\langle v_y \rangle /\lambda.
  \end{equation}
  %Juniper %REF 53
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}.
  When velocity
  is mode-locked to %repeat periodically
  a spatial location
  a closed loop appears in  
  phase space. % showing the relationship
  %between two periodic functions
  The pattern is determined by the mode,
  or frequency ratio,
  so a 1:1 mode appears as a circle or oval.
  Nodes appear in the oval 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is not fully phase locked
  will apppear as an unclosed loop.
  Such quasiperiodic systems are
  not fully synchronized.
  %and the shifts in phase space represent
  %small changes in system behavior.
  With a long simulation time,
  a quasiperiodic phase diagram
  fills the plotting region due to the gradual shift
  in the velocity-position relationship.
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  %\footnote{The term phase
  %has two scientific meanings:  
  %oscillation phase $\phi_0$ is the constant of the argument
  %in a periodic function
  %$\sin{(\omega t + \phi_0)}$ and phase space is
  %used to characterize oscillating systems with
  %parametric plots.}.

@@

  In Fig.~\ref{fig:hops}
  we show the effects of lowering the frequency
  of applied driving force,
  holding the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  since $F^{dc} - F^{ac}= 0.05$
  is too small to overcome $A_p$.
  The number of forward steps 
  $n_f$ increases as frequency decreases.
  Low frequencies
  result in sustained positive or negative motion of a particle,
  where in Fig.~\ref{fig:hops}(e)
  the particle reaches the top edge of the system
  and wraps back to $y=0$.
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency as marked.
        In (e) the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  Experiments with single colloids \cite{Juniper2015} 
  show 
  hopping patterns with backward steps are more difficult
  to achieve than forward,
  with $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  were realized 
  for a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
  {\bf Find the parameters
  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
  %[well, go one...]
  In Fig.~\ref{fig:hops_back}
  we fix $f=0.01$, $F^{dc}=0.1$, and and $A_p = 0.1$.
  We show the results for increasing $F^{ac} = 0.2, 0.3, 0.4$.
  %of the system for our original parameters.
  Here the number of backwards steps
  $n_b$ increases from $n_b = 0$ in (a) to
  $n_b = 2$ in (b) to $n_b = 4$ in (c).  
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

    \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        Mode-locked steps in $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with frequency $f=0.01$ and $F^{ac}=0.4$.  At low values of $F^{dc}$ the particle may move backwards, distorting the steps.
      }
      \label{fig:shapiro}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item

>>>>

We use a classical model for 
studying the dynamics of $N$ interacting particles,
using the net force on each particle to calculate
its trajectory.
Particles are confined in a two-dimensional (2D) 
simulation of area $A = L \times L$ where $L=36.5 a_0$
where $a_0$ is a dimensionless unit of length.
An individual particle $i$ has
position $\vec{r}_i = x_i \hat{x} + y_i \hat{y}$
and velocity $\vec{v}_i = d\vec{r}_i/dt$.
The edges of the system are treated with
periodic boundary conditions
such that a particle leaving the edge of the system is mapped
back to a position within the simulation boundaries 
by the transformation $x_i+L \rightarrow x_i$ and $y_i+L \rightarrow y_i$.
%and particles interact across PBC.
We show a schematic of the system in Fig.~\ref{fig:landscape0}(a).
The units of the simulated variables are summarized in Table ~\ref{tab:1}.

@@

The molecular dynamics simulation is controlled by a $for()$ loop
which runs from an initial to maximum integer number of time steps.
%$t_i$.
Each integer time step interval %$t_{i+1}-t_i$
represents a simulation time of $\Delta t$ 
simulation units $\tau$.  %as described in Table 1
At each time step
we evaluate the net force on each particle as a function of its position
$\vec{r}_i(t)$
and then integrate
the equation of motion to move particles
to an updated position.
%$\vec{r}_i(t+\Delta t)$.%
Since the acceleration as zero,
the integration of the equation of motion
is performed via 
the Euler method 
\begin{equation}
  \vec{r}_i(t+\Delta t) = \vec{v}_i(t) \Delta t + \vec{r}_i(t)
    \label{eq:euler}
\end{equation}
for a small time step $\Delta t = 0.01 \tau$.
In %Section~\ref{sec:problems}
Exercise~\ref{ex:euler}
we describe 
the numerical methods for 
solving differential equations.
%

\begin{table}[h!]
\centering
\caption{Simulation parameters and units and comparable
  experimental values~\cite{Juniper2015}.
  Blanks %in the experimental parameters
  indicate
  units, rather than parameters that
  are not easily represented by a single value.}
%{\it might be more appropriate to match Juniper parameters more precisely given our focus...}}
\begin{ruledtabular}
\begin{tabular}{c c c } %p{5cm}}
Quantity & Simulation Unit & Experimental value\\
\hline
length &  $a_0 = 1$ & $ a_0 \sim 1.5 \mu m$\\
energy & $E_0 = 1$ & \\ %$ < E_0 <$ \\
%electric potential & $V(r_{ij}) = E_0/r_{ij}$ \\
%energy & $E_0 = q^2{Z^*}^2/4\pi \epsilon \epsilon_0 a_0$ \\
%dimensionless interaction strength & $q$ \\
%effective colloidal charge & $Z^*$ \\
%solvent dielectric constant & $\epsilon \epsilon_0$\\
force & $F_0 = E_0 / a_0$ & \\ %$<F_0<$\\
time &  $ \tau = \eta a_0 / F_0 $ \\ %& $ < \tau <$\\
velocity &  $ a_0 / \tau $ &  $v \sim 5 \mu m/s $\\
driving period & $T = 100 \tau$ & $T \sim 1.3$ s \\
viscosity coefficient & $\eta = F_0 \tau / a_0 $ & $\eta \sim 10^{-3}$ Pa-s \\
%juniper uses water–ethanol mixture
substrate period & $\lambda = 1.825 a_0$ & $\lambda = 3.5 \mu m$ \\
substrate amplitude & $U_0 = 0.058 E_0$ & $U_0 = 75 k_B T \sim 2 J$ \\
%A_p = 0.1 = N_p pi U_0/L.  this is how calculated U_0
temperature & $T_0 = 0$ \footnote{to learn more about the effects
  of temperature on this simulation
  see Ex.~\ref{ex:brownian} where we study the limit
  $U_0 \sim k_B T$.} & $T \sim 300K $ \\

@@

Here we drive 
a single particle %on this landscape
%responds to the applied driving force
%by moving
across the landscape %maxima
to characterize its motion.
%synchronized with 
%the period of $F^D(t)$.
%applied driving force.
%along the y-direction
%({\it redundant, just refer back to eq. in Model?})
%and $V_{0y}=0.2$.
%This is illustrated in Fig.~\ref{fig:1}(a) where
%the red (blue) regions show local maxima (minima).
%
The numerical implementation of the landscape 
is calculated with Eq.~\ref{eq:ysubstrate} as 
\begin{equation}
  \label{eq:force}
  F^l_y(y) = -A_{p} \sin{(N_p \pi y / L)} 
\end{equation}
where the force is scaled with parameter $A_{p} = N_p \pi U_0/L$.
In this section we fix the landscape parameters
to $A_{p} = 0.1 F_0$ %force units
with $N_p=20$ minima %in the landscape
corresponding to a spatial period $\lambda = 1.825 a_0$.

%In Fig.~\ref{fig:0} 
The driven particle %adjusts
moves across %its motion to traverse
the periodic landscape with the same rhythm as 
the applied time-dependent force $F^D(t)$.
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape,
and 
the particle hops between minima in the energy landscape.
%
In Fig.~\ref{fig:0}(a)
we plot $F^D(t)$ %defined in Eq.~\ref{eq:drive}.
as a function of time with
%The time independent
constants $F^{dc}=0.1$, 
$F^{ac}=0.05$ and $f=0.01$ cycles per time unit $\tau$.
The temporal period of the driving force is
$T = 1/f = 100 \tau$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%RAMP
%To avoid transient oscillations at early times, the dc driving force is initially zero and slowly increased %$F^{dc}$. at a rate of $\Delta F^{dc} = 0.01$ every $\Delta t = 4$ time units  to the constant value $F^{dc}=0.1$. In Fig.~\ref{fig:0}(a) we plot $F^{dc}$ in blue to show the increase in  $F^{dc}$ for the first $40$ time units In orange we show  the combined ac and dc drive $F^D(t)$ when the magnitude of the ac applied force is initially zero.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%since $\sin{(0)}=0$.
We mark the maxima of $F^{ac}(t)$
with the
vertical dashed lines %in panels (a) and (b)
-- i.e. $\sin{(\omega t)} = 1$.
%
%
%with the initial driving force at is minimum value 
%$F^D(0) = F^{dc}$. 
%
In Fig.~\ref{fig:0}(b) 
we show the $y-$position of the particle
as a function of time.
We 
normalize $y$ by $\lambda$ %, the spatial period of the potential
to show  particle motion between substrate minima.  
The initial particle position is $y = 0 $. %1 a_0$,
%where the $F^l$ is negative.
%JUST BECAUSE
%causing the particle to move to
%a landscape minima at the start of the simulation.
As the driving force increases,
%the effects of the landscape become less obvious,
the motion of the particle
synchronizes with the driving period $T$.
We measure 
average particle velocity $\langle{v}_y\rangle$
as the displacement %$\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
The particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ over the time period $T$,
with 
the average velocity 
$\langle {v}_y \rangle= 2 \lambda f$. % where $T = 1/f$.
The horizontal dashed lines
coincide with the condition the particle is at a substrate minima
where substrate force  $F^l = -A_p$,  
i.e. $\sin{(\pi y / \lambda)} = 1$.
%or $\pi y / \lambda = m \pi/2$, where $m = 1, 5, 7$, {\it etc.}
%Once the particle motion
%coincides with the applied drive,
%indicating synchronization,
The particle synchronizes its motion such that the 
driving force is maximum when the landscape 
force is minimum,
as indicated %with the coincidence of 
with the intersection of
vertical and horizontal lines.  
%i.e. the particle position $y/\lambda$.  
The slope of $y/\lambda$
is proportional to the net force on the particle.
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $. 
\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{single_particle.pdf}
\caption{(a) The applied driving force $F^D(t)$. % (Eq.~\ref{eq:drive}).
  %where the parameter $F^{dc}$ (blue) is slowly increased from zero %to a constant value %as described in the text.
  (b) 
  The $y-$position of the driven particle
  %of a single driven particle
  normalized by the period of the substrate $\lambda$.
  %as a function of time
  }
\label{fig:0}
\end{figure}
\end{center}

The competition between the driving force and landscape potential
can produce a variety of hopping patterns in the particle motion. 
%In Fig.~\ref{fig:0}
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
%single dc case with figure
%dc_current 0.01
%ac_current 0.05
%ac_frequency 0.01
%fp_y 0.1
%
The relative values of $F^{ac}$, $F^{dc}$ and $A_p$
control the rate and distance a  particle moves 
forward and backward in the landscape.

  It is useful to compare
  mode-locked quantities %periodic signals
  in a two dimensional phase plot.
  In a non-driven system, an appropriate
  phase space is particle velocity $v_y$ versus position $y$.  
  In a system driven parallel to the $y-$direction,
  %the particle velocity and position increase
  %in time. % due to $F^{dc}$.
  %Since a system does not form
  %a closed loop in
  %$v_y$ vs $y$ space,
  we define phase variables 
  to account for the net increase in velocity
  and position.
  The phase position is
  defined as 
  %within the substrate period as 
  %We define a phase variable 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \phi(t) = 2\pi(y(t)-\langle v_y \rangle t)/\lambda
  \end{equation}
  centered about the average particle velocity $\langle v_y \rangle$
  and normalized by the substrate period $\lambda$ \cite{Juniper2015}.
  We plot this phase
  versus the phase velocity 
  \begin{equation}
    %(y mod \lambda) / \lambda
    \dot{\phi}(t) = 2\pi(v_y(t)-\langle v_y \rangle /\lambda.
  \end{equation}
  %Juniper %REF 53
  %and easily generated with a computer code 
  %or oscilloscope \cite{Tong1997}.
  When velocity
  is mode-locked to %repeat periodically
  a spatial location
  a closed loop appears in  
  phase space. % showing the relationship
  %between two periodic functions
  The pattern is determined by the mode,
  or frequency ratio,
  so a 1:1 mode appears as a circle or oval.
  Nodes appear in the oval 
  for higher modes,
  sometimes forming figure-eights
  or other recognizable patterns.
  A system that is not fully phase locked
  will apppear as an unclosed loop.
  Such quasiperiodic systems are
  not fully synchronized.
  %and the shifts in phase space represent
  %small changes in system behavior.
  With a long simulation time,
  a quasiperiodic phase diagram
  fills the plotting region due to the gradual shift
  in the velocity-position relationship.
  %with a frequency generator,
  %where two combined frequencies at perpendicular orientations
  %\footnote{The term phase
  %has two scientific meanings:  
  %oscillation phase $\phi_0$ is the constant of the argument
  %in a periodic function
  %$\sin{(\omega t + \phi_0)}$ and phase space is
  %used to characterize oscillating systems with
  %parametric plots.}.

@@

  Fig.~\ref{fig:hops}
  shows the effects of lowering the frequency
  of applied driving force
  We hold the remaining parameters fixed 
  to 
  $F^{dc}=0.1$, $F^{ac}=0.05$, and $A_p = 0.1$.
  We observe no backward steps 
  ($n_b = 0$) 
  across a broad range of frequencies
  since $F^{dc} - F^{ac}= 0.05$
  is too small to overcome $A_p$.
  The rate of forward hops 
  increases as frequency decreases,
  but in each case the particle
  hops across two substrate periods as in Fig.~\ref{fig:0}.
  In Fig.~\ref{fig:hops}(a-b) the particle hopping rate
  do not match the temporal period of $F^D(t)$
  due to the high frequency.
  In Fig.~\ref{fig:hops}(a) the high frequency $f= 0.1$
  is apparent in the undulations of the particle
  with a period of $10\tau$.
  %Due to the high frequency,
  The particle is trapped between substrate minima $y \approx \lambda/2 $ for
  a time interval of $400 \tau$.
  In Fig.~\ref{fig:hops}(b) the frequency $f= 0.05$
  with a period of $20\tau$
  arrests the particle between minima,
  with a hopping rate of $200 \tau$.
  At intermediate frequencies 
  such as $f=0.01$
  the particles are synchronized so that 
  the hopping rate matches the driving frequency.
  In Fig.~\ref{fig:hops}(c) $f=0.015$
  the particle hops forward two minima every $67\tau$.
  Low frequencies
  result in sustained positive motion of a particle.
  In Fig.~\ref{fig:hops}(d) $f=0.005$
  the particle executes two subsequent forward hops
  before becoming trapped
  for the remainder of the period $200 \tau$.
  In Fig.~\ref{fig:hops}(e) $f=0.001$
  the hopping is continuous
  over the simulation time.
  Here the particle reaches the top edge of the system
  and wraps back to $y=0$.
  Given a simulation time of the period length $1000 \tau$,
  the particle would cease forward motion.
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig5}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc} = 0.1$ and $F^{ac} = 0.05$ as Fig.~\ref{fig:0} and decreasing frequency $f=$ (a) $0.1$,
        (b) $0.05$, (c) $0.015$, (d) $0.005$ and (e) $0.001$ where  
        the particle wraps the periodic boundary conditions.
      }
      \label{fig:hops}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}

  Experiments with single colloids 
  show 
  hopping patterns with backward steps are more difficult
  to achieve than forward.
  In Ref.\cite{Juniper2015} the following
  combinations of forward and backwards steps where realized:
  $n_f = 0$ to $6$ for $n_b = 0$,
  $n_f = 0$ to $5$ for $n_b = -1$,
  and
  $n_f = 2$ to $3$ for $n_b = -2$
  %were realized 
  by sweeping through
  a variety of applied forces parameters $F^{dc}$ and $F^{ac}$.
  {\bf Find the parameters
  that create hopping patterns similar to those in Ref.~\cite{Juniper2015}}.
  %[well, go one...]
  In Fig.~\ref{fig:hops_back}
  we fix $f=0.01$, $F^{dc}=0.1$, and $A_p = 0.1$.
  We show the results for increasing
  the amplitude of $F^{ac} = 0.2, 0.3, 0.4$.
  %of the system for our original parameters.
  Here the number of backwards steps
  $n_b$ increases from $n_b = 0$ in (a) to
  $n_b = 2$ in (b) to $n_b = 4$ in (c).
  The number of forward steps also increases
  due to the increased total positive amplitude of $F^D(t)$.
  \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{parameters_fig6}.pdf}
      \caption{
        Motion of a particle with the same values of $F^{dc}$ and frequency as Fig.~\ref{fig:0} and increasing $F^{ac}$.
        (a) The particle moves forward six minima with no steps backward.
        (b) The particle moves forward eight minima with two steps backward.
        (c) The particle moves forward nine minima with four steps backward.
      }
      \label{fig:hops_back}
    \end{figure}
  \end{center}

  In Fig.~\ref{fig:shapiro}
  we show two additional sweeps of $F^{dc}$.
  In Fig.~\ref{fig:shapiro}(a) $F^{ac}= 0.0$.
  With no oscillating component of the driving force,
  the force-velocity relationship is monotonically increasing
  above the depinning threshold $F^c$ such that
  \begin{equation}
    \langle v_y \rangle \propto (F^{dc}-F^c)^{-\beta}
  \end{equation}
  The particle does not phase lock since there is no periodicity to $F^D(t)$,
  but does exhibit undulations in $\langle v_y \rangle$
  due to the corregations in the substrate.
  In Fig.~\ref{fig:shapiro}(b) $F^{ac}=0.4$ and frequency $f=0.01$.
  Mode-locked steps in $\langle v_y \rangle$ vs. $F^{dc}$
  At low values of $F^{dc}$ the particle may move backwards,
  distorting the steps, as seen below $F^{dc}<0.3$
  Between $0.3< F^{dc}<0.5$ the system exhibits phase locked steps.
    \begin{center}
    \begin{figure}[h!]
      \centering
      \includegraphics[width=\columnwidth]{{fig9_sweep_FDC_vs_vx}.pdf}
      %\includegraphics[width=\columnwidth]{{fig7_sweep_FDC_vs_vx}.pdf}
      \caption{
        $\langle v_y \rangle$ vs. $F^{dc}$ of a particle with
        $F^{ac}=0.0$ (blue) and $0.4$ (orange) with frequency $f=0.01$.
      }
      \label{fig:shapiro}
    \end{figure}
  \end{center}
  %In Fig.~\ref{fig:hops}
%\item Frenkel-Kontorova and competing length scales for low temperature systems where thermal fluctuations are negligible
%  \item The Fokker-Planck Equation
%  \item Aubrey-Kontorova + commensurability
%  \item nanotribology
 %   kink motion
 %   Vanossi et al J.Phys.: Condens. Matter 19 (2007)
  %\item
